\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{dirtytalk}
\usepackage{amssymb}
\usepackage{fancyhdr}
\lhead{Reveal of a Li(f)e}
\rhead{Page \thepage}
\cfoot{computer-cat1}
\pagestyle{fancy}
\title{The Reveal of a Li(f)e}
\author{A gift for Alan Grey}
\date{Screenplay by Kevin Varrow and Ivan Flores}
\begin{document}
\maketitle
\thispagestyle{fancy}
\tableofcontents
\section[$\mathbb{IMPORTANT\ NOTE}$]{$\mathbb{IMPORTANT\ NOTE\ FOR\ CONTRIBUTORS}$}
\textbf{This document's contents, authors, and table of contents as well as the authors' age, 
gender identity, and especially orientation is classified to security level $\mathbb{IV}$}

\noindent
\textbf{No portion of this document below the line that is longer than four words may be spoken publicly, shared on 
Discord or Telegram, or otherwise publicly transmitted in any way with out direct permission from Mistrum Alan Grey.}

\noindent
Copyright MMXXII Mistrum Alan Grey

\vspace{5mm}
Feel free to sign your tag in the space here. \vspace{2mm}

\noindent \texttt{Stay Alive |-/} (Twenty Øne Pilots) \vspace{2mm}

\noindent \emph{Trust no one after dark} (Alan xemself) \vspace{2mm}

\noindent You're only a bad guy on the surface. Theres more to you, even if only I can see it, its there. (Joshy Montero) \vspace{2mm}

\noindent You be who you want to be. If anyone says otherwise, they can go f*** themselves. (Ed Sheeran) \vspace{2mm}

\section{Opening music}
To get the crowd in the mood for something big to happen, Shy Away will play as the first song.
Next up is The Outside to keep it going. The next song would be Mulberry Street (Live)
mainly for the line \say{Keep your bliss! There's nothing wrong with this!} The last normal
song is Level of Concern (Live from Outside). Alan will sing the refrain through the door.

The final song is No Chances which has complex choreography, mainly just to build Alan's
confidence. Alan walks in, glasses on. When the courus starts, he sticks his arms out, 
imitating the TØP Trident. When the seccond courus hits, xi \say{drops dead} for lack 
of a better term.

\noindent \rule{\textwidth}{4pt}

\noindent \begin{center}DO NOT SCROLL PAST THIS LINE\end{center}

\noindent \rule{\textwidth}{4pt}
\newpage

\section{Just in Case: TF}
%Section O
Note: This section is to be used ONLY if questions about TF are asked.

I thought you already knew this but I am prepared to explain it if i must\ldots{}

TF is short for transformation, but its not that clear cut. Although it is a very broad topic,
I will try my best to be narrow-scope. The kink itself is TransFur and was originally ment to
be people turning into their sonas but it quickly got twisted into meany varients. Pokemon
swapping bodies, and then turning into a couch, melting into goo, people turning into dragons
and dragons turning into airplanes, the list goes on and on. I will show examples later,
right now, I gotta get back on track.

\section{Plush TF}
% I
Im going to start where Ivan once started. Plush TF! Its exactically what it sounds like.
Someone, typically a traditional 'sona but not a human, is turned into a plush version of themself.
Thi sidea has been done to death. (Criz's plush TF trade with TwinkleFluff) as you can clearly see.

Its cool and all, but how can we take it a step closer>

\section{Pokemon TF}
% II
Pokemon TF is much cooler. People turning into Pokemon, Pokemon swaping peices of themselves
Here. I'll just show you.

\section{CrizBN}
% III
(TF Tuesday: Cupcakes and Smol Snakes!)\\
I guess cupcakes and smol snakes are related! 

\noindent
(A ''Plane`` Simple TF) \\
I mean, he asked for wings, he got wings.

\noindnet
(Cris, latest REF) \\
They are make by CrizBN. He is a shiny mew that can't keep his magic to himself. IRL, he
is an aerospace enthusiast. That means he likes air/space-craft. (Look at his scarf!)

(OcTransFur - Snowy in the Space station) One of his character is a snow lepord named Snowy

(Unexpected Landing) Sometimes he becomes snowy without knowing it.

\section{IX-TF}
% IV

\section{Intermission}
R.I.P. to my Youth - The Neighborhood

\section{LF-IX}
% V

\section{BetaEtaDelota}
% VI

\section{GrantJoey}
% VII

\section{IX}
% VIII

\section{PM-IX}
% IV

\section{Poipole98 - How we met}
% X

\section{Intermission}
Alone Again - The Weeknd

\section{Kirim and Void}
% XI

\section{RP}
% XII

\section{SnivyTypes}
% XIII

\end{document}
